GPU-friendly Stroke Expansion

### 2024-06-13 paper.tex
Address reviewer #1's feedback on Section 8
This largely addresses the first reviewer's feedback on Section 8,
particularly the following asks:

1. Section 8.1 expands on the broader renderer architecture that the
   flatten stage was integrated into, clarifying the sorting
   requirements on line soup.

2. Added a new figure to illustrate the pipeline with broad strokes,
   breaking it into "input processing", "flattening", and
   "rasterization" blocks.

We aimed to satisfy the following the criteria:
\begin{enumerate}
  \item The implementation must be able to handle a large number of inputs at real-time rates. 
  \item The stroke outlines must meet the strong correctness definition.
  \item The implementation must support the standard SVG stroke end cap (\emph{butt}, \emph{square}, \emph{round}) and join styles (\emph{bevel}, \emph{miter}, \emph{round}).
  \item The CPU must do no work beyond the basic preparation of the input path data for GPU consumption.
\end{enumerate}

@@

% TODO: - Watertightness

@@

A property of the data-parallel structure is that the output is unordered. The cubic-Bézier-to-Euler-spiral conversion is sequential within a single thread, so it is possible to preserve ordering at the scope of an individual path segment, if desired. However, ordering cannot be guaranteed across path segments. We refer to this output data structure as \emph{line soup}. We integrated the compute shader as a stage in a larger compute shader pipeline (discussed in Section \ref{subsection:gpu-results}) that spatially sorts the line soup in subsequent binning and tiling stages prior to rasterization.

>>>>

We aimed to satisfy the following the criteria:
\begin{enumerate}
  \item The implementation must be able to handle a large number of inputs at real-time rates. 
  \item The stroke outlines must meet the strong correctness definition.
  \item The implementation must support the standard SVG stroke end cap (\emph{butt}, \emph{square}, \emph{round}) and join styles (\emph{bevel}, \emph{miter}, \emph{round}).
  \item The CPU must do no work beyond the basic preparation of the input path data for GPU consumption, in order to maximize the exploited parallelism.
\end{enumerate}

@@

@@

A property of the data-parallel structure is that the output of the compute stage is unordered. The cubic-Bézier-to-Euler-spiral conversion is sequential within a single thread, so it is possible to preserve ordering at the scope of an individual path segment, if desired. However, ordering cannot be guaranteed across path segments. We refer to this output data structure as \emph{line soup}. An application may want to sort the line soup, depending on the requirements of the chosen rendering algorithm. For instance, our own renderer employs tile-based scanline rasterization in a compute shader, with a pipeline architecture that resembles \emph{cudaraster} (\citet{Laine2011}) and \emph{MPVG} (\citet{Ganacim2014}). In this design, the line soup elements are spatially sorted by subsequent compute stages into a grid of 16x16 pixel tiles. The final compute stage of our renderer (called \emph{fine rasterizer}) operates at tile granularity and computes pixel coverage for filled polygons outlined by the line soup (the details of which are beyond the scope of this paper).

\begin{figure*}
    \includegraphics[scale=0.275]{pipeline}
    \caption{We integrated our curve flattening shader into our own renderer implemented entirely in compute shaders. The flattening stage (described in Section~\ref{section:gpu-impl}) converts stroked paths to filled outlines and flattens them into an unordered soup of line segments. Our renderer spatially sorts the line soup into tiles before computing pixel coverage using a highly parallel scanline rasterizer.}
    \Description{Our GPU pipeline architecture in broad strokes}
    \label{fig:pipeline}
\end{figure*}
